Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
Related to #22. Highlighted the differences with the previous works, plus re-writing because what was already written was simply not true. Please @JJ @fergunet @pacastillo review before closing

This work introduces a recently released system named
MUSES, from Multiplatform Usable Endpoint Security, which is a
dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a
set of security rules defined as specifications of the Corporate
Security Policies. In addition, it has the ability of `learning' from the user's (the employees)
past behaviour and adapt the set of rules, or even inferring new ones,
in order to deal with potential security incidents that they might cause in the future. 
Then the system reacts, in a non-intrusive way, to the potentially
dangerous sequence of actions (events) that the employees are conducting at
any time. The MUSES system has been also tested in an actual company, with satisfactory results. The analysis of all data from these tests, and conclusions, are part of the future work.

To this end, MUSES analyses the users' behaviour by means of Data
Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
(ML) methods \cite{MachineLearning_Bishop06}, extracting a set of
patterns which is later processed by means of Computational
Intelligence (CI) algorithms, namely Evolutionary Computation methods
\cite{EAs_Back96,GP_Koza92}. The general ideas behind MUSES were
already presented in
\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
the implementation was in its early stages when those papers were
submitted. After the release of the first prototype, an additional
work on the data mining techniques was conducted in \cite{mora14:urls} so that we have a
clearer idea of MUSES capabilities and, as such, they will be presented in
this paper.

>>>>

This work introduces a recently released system named
MUSES, from Multiplatform Usable Endpoint Security, which is a
dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a
set of security rules defined as specifications of the Corporate
Security Policies. In addition, it has the ability of `learning' from the user's past behaviour and adapt the set of existing rules, or even inferring new ones,
in order to deal with potential security incidents that they might cause in the future. 
Then the system reacts, in a non-intrusive way, to the potentially
dangerous sequence of actions \footnote{Which are treated as `events' inside the system.} that the employees are conducting at
any time. The MUSES system has been also tested in an actual company, with satisfactory results. The analysis of all data from these tests, and conclusions, are part of the future work.

To this end, MUSES analyses the users' behaviour by means of Data
Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
(ML) methods \cite{MachineLearning_Bishop06}, extracting a set of
patterns which is later processed by means of Computational
Intelligence (CI) algorithms, namely Evolutionary Computation methods
\cite{EAs_Back96,GP_Koza92}. The general ideas behind MUSES were
already presented in
\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
the implementation was in its early stages when those papers were
submitted. Also, an additional work on the data mining techniques was conducted in \cite{mora14:urls}, over a set of data previous to the release and test of the first MUSES prototype. As there was no available test data, a set of URL connection logs were provided by a Spanish company, as well as both black and white lists. These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees. By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, could be presented at \cite{mora14:urls}. Now, after the release of the first prototype, along with the first conducted tests, we have a clearer idea of MUSES capabilities and, as such, they will be presented in this paper.
